gij bent 2

### 2025-09-28 paper/paper.qmd
Fix small typo
Add overview of eliminated and non-eliminated coefficients

First, we will look at the coefficient globally. The density plot of the variation coefficients in @fig-general-density gives a global overview of the how each language user "deviates" from what is expected given their gender, location etc.. Negative coefficients on the left side of the plot show deviations of individual language users towards the conservative *gij zijt*. Positive coefficients on the right side of the plot show deviations of individual language users towards the innovative *gij bent*. The middle dotted line marks the zero coefficient, i.e. those who do not deviate from the expected norm. We see that there is a bi-modal distribution in the variation coefficients. The first distribution shows many slight corrections towards the conservative form (first bump). The second distribution shows a smaller number of larger corrections towards the innovative form (second bump). This bi-modal variation pattern would have remained invisible in a more traditional regression model.

>>>>

Of the `r num_users_filtered %>% formatn` unique tweet authors in our dataset, our elastic net regression was able to estimate `r coefficients %>% filter(coefficient != 0) %>% dim %>% .[1] %>% formatn` innovation patterns. This means that `r coefficients %>% filter(coefficient == 0) %>% dim %>% .[1] %>% formatn` authors either did not meaningfully deviate in their *gij bent* or *gij zijt* usage from what is expected from them. It could also be that the model did not have enough data to reliably estimate an innovativeness score, but since we imposed a lower limit of 10 attestations per user, this should generally not be the case.

The density plot of the variation coefficients in @fig-general-density gives a global overview of the how each language user "deviates" from what is expected given their gender, location etc.. Negative coefficients on the left side of the plot show deviations of individual language users towards the conservative *gij zijt*. Positive coefficients on the right side of the plot show deviations of individual language users towards the innovative *gij bent*. The middle dotted line marks the zero coefficient, i.e. those who do not deviate from the expected norm. We see that there is a bi-modal distribution in the variation coefficients. The first distribution shows many slight corrections towards the conservative form (first bump). The second distribution shows a smaller number of larger corrections towards the innovative form (second bump). This bi-modal variation pattern would have remained invisible in a more traditional regression model.
